\documentclass{resume} % Use the custom resume.cls style
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Qian Xu} % Your name
\address{+86 15600616741 \\ drqianxu@163.com}  % Your phone number and email

\begin{document}

\begin{rSection}{Summary}

{8+ years of experience in AI inference optimization on NPU/GPU, spanning model quantization, CUDA kernel development, compiler design, and software-hardware co-design.}

\end{rSection}


\begin{rSection}{Education}

{\bf Ph.D. of Electronics Engineering} \hfill {2013 - 2018}
\\ 
University of Chinese Academy of Sciences. Outstanding Graduates

{\textbf{Bachelor of Electronics Engineering}}  \hfill 2009 - 2013\\
Southeast University.


\end{rSection}

\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C++, CUDA \\
Frameworks & PyTorch, TensorRT-LLM, vLLM, CUTLASS, MLIR \\
Domain & Model Quantization, Kernel Optimization, NPU/GPU Architecture, Compiler Design
\end{tabular}
\end{rSection}

\begin{rSection}{Professional Experience}

\noindent



\textbf{Edge AI Inference Optimization (AD/VLM/VLA)} \\ % Job title
\textit{AI Software Architect of Edge Computing Group} \hfill Alibaba PTG \hfill 2024 Q4 -- Present

\vspace{4pt}

Focused on inference acceleration and model optimization for AD/VLM/VLA workloads on edge devices, targeting deployment on custom GPGPU-based AI accelerators.

\begin{itemize}

\item \textbf{Model Quantization and Compression}:\newline
Led low-bit quantization research and deployment for VLM/VLA/LLM, covering algorithm design, accuracy optimization, and inference acceleration.
\begin{itemize}
  \item \textbf{Qwen-VL}: Applied \textbf{AWQ}, \textbf{SmoothQuant}, \textbf{GPTQ}, and \textbf{SpinQuant} to quantize to \textbf{FP4} (weights + activations). Achieved higher accuracy than the W4A16 baseline while reducing \textbf{Prefill} latency by 50\%. Integrated \textbf{Eagle} speculative decoding for up to $\sim$4.7$\times$ decoding speedup.
  \item \textbf{Orion} (VLA): Combined \textbf{Spin + Scale + SVD decomposition + Mixed precision} to retain accuracy of FP4 model. Achieved $>$15\% latency reduction compared to FP8 baseline.
  \item \textbf{RDQuant} -- Rate-Distortion Optimal Mixed-Precision Quantization:
  Proposed a per-output-channel mixed-precision framework based on \textbf{rate-distortion optimization}, using Lagrangian relaxation to allocate bit-widths (\textbf{NVFP4}/\textbf{FP8}/\textbf{FP16}) under a given bit budget. Designed mixed-precision GEMM pipeline with channel regrouping, weight repacking, and multi-format kernel dispatch. On \textbf{Qwen3-4B}, achieved lower perplexity than the BF16 baseline at $\sim$5.3 bits/weight. Integrated into \textbf{vLLM} with \textbf{1.9$\times$} speedup over FP16 on \textbf{NVIDIA RTX 5090}.
  \item \textbf{Entropy-Aware Compression for Hardware Compression IP}:
  Developed weight and KV cache compression techniques targeting backend hardware compression IP. For weights, proposed per-block FP8 scale optimization jointly minimizing MSE and codeword entropy, achieving $\sim$12\% compression on NVFP4 with no accuracy loss. For KV cache, proposed a low-entropy FP16 representation via orthogonal rotation and Lloyd-Max quantization, enabling hardware-transparent compression equivalent to $\sim$3-bit without custom dequantization kernels.
  \item Conducted joint software-hardware evaluation of \textbf{Microscaling FP4} and \textbf{NVFP4} to guide quantization hardware roadmap.
\end{itemize}

\item \textbf{Kernel Development and Operator Optimization}:
Developed and optimized CUDA kernels on custom GPGPU to accelerate model inference.
\begin{itemize}
  \item \textit{Autonomous Driving Operators}: Optimized performance-critical ops including \textbf{DeformableAttention}, \textbf{GridSample}, \textbf{Voxelization}, \textbf{BevPoolv2}, \textbf{CoordTransformMatrix}, etc. E.g., reduced \textbf{DeformableAttention} latency to $\sim$1/6 of MMCV baseline.
  \item \textit{LLM Operators}:
  \begin{itemize}
    \item \textbf{W4A16 Inference Optimization}: Optimized \textbf{W4A16 GEMV} kernels for decode-stage shapes (especially $M\!=\!1$), achieving $\sim$80\% memory bandwidth utilization. Implemented fused \textbf{SwiGLU-FFN} kernel on Marlin backend by reinterleaving gate/up projection weights to enable \textbf{GeLU + Mul fusion at register level}, eliminating intermediate memory round-trips.
    \item Integrated \textbf{MoE W4A16} kernel into internal \textbf{TensorRT-LLM} pipeline, including offline weight repacking and graph integration. Enabled end-to-end deployment of \textbf{Qwen3-MoE}.
    \item \textbf{FP8 GEMM} optimization: Added support for K-dimension alignment to multiples of 48 in \textbf{CUTLASS} to enable 1.5$\times$ throughput feature at PTX level. Fixed TMA store partial-write issue that caused 2$\times$ write traffic overhead.
  \end{itemize}
\end{itemize}

\item \textbf{Cross-Platform Profiling, Performance Analysis, and Hardware Co-Design}:
Performed architecture analysis, deployment, and benchmarking of latest-generation VLMs across \textbf{NVIDIA Thor} and custom \textbf{GPGPU}-based edge SoC. Used \textbf{Nsight Systems} and \textbf{Nsight Compute} (internal build) for end-to-end latency profiling and operator-level bottleneck analysis of critical ops in key models, driving hardware requirement definitions.
\begin{itemize}
  \item Analyzed network architecture of \textbf{Qwen2.5-VL}, \textbf{Qwen3-VL}, and \textbf{Qwen3-Omni}. Deployed and benchmarked on both platforms with end-to-end latency profiling and operator-level bottleneck analysis.
  \item Conducted bottleneck analysis on \textbf{Deformable Attention} in VAD-Base, derived the \textbf{double ALU} requirement with quantitative performance gain estimation and delivered to GPGPU team as edge SoC design input.
  \item Analyzed hardware optimization options for \textbf{Flash Attention} during LLM Prefill stage, quantitatively evaluated the \textbf{double SFU} benefit and delivered as SoC design input.
\end{itemize}

\end{itemize}


\textbf{NPU Software Architecture Design} \\ % Project or Role Title
\textit{AI Software Architect, Movidius NPU Team} \hfill Intel \hfill 2022 Q1 -- 2024 Q4

\vspace{4pt}

Contributed to the co-design of software and hardware architecture across multiple generations of Intel's Movidius NPU product line, focusing on compiler prototyping, advanced compilation techniques, and hardware/software co-optimization.

\begin{itemize}

\item \textbf{Prototype Compiler Development}:
Led the development of a prototype compiler to interface with backend hardware simulators for accurate and reliable model performance simulation.
\begin{itemize}
  \item \textbf{Hardware Change Validation}: 
  Evaluated the software stack impact of proposed hardware changes for future NPU generations. Integrated with hardware simulators to test architectural trajectories and identify those with improved PPA.
  
  \item \textbf{KPI Definition and Bottleneck Analysis}: 
  Defined key performance indicators using internal profiling toolsets. Analyzed performance bottlenecks in customer workloads (e.g., Microsoft, HP) to inform compiler feature planning and hardware evolution.
  
  \item \textbf{Model Coverage and Stability}: 
  Achieved support for over 800 models with 90\%+ coverage of Intel Open Model Zoo, ensuring broad compatibility and robustness.
\end{itemize}

\item \textbf{Advanced Compilation Technique Development}:
Explored cutting-edge compilation techniques to improve inference efficiency on NPUs. Collaborated with production compiler and DirectML teams to deliver transferable insights.
\begin{itemize}
  \item \textbf{LLM Performance Optimization}: 
  Optimized LLM inference through mixed precision, FlashAttention, task pipelining, and memory-efficient FFN tiling.
  
  \item \textbf{Tiling and Fusion}: 
  Developed automatic layer fusion algorithms for cross-component execution. Implemented double buffering for conflict-free scheduling.
  
  \item \textbf{Resource Allocation and Scheduling}: 
  Designed algorithms for efficient compute/memory resource allocation with reduced spilling. Developed prefetch scheduling to overlap communication and computation.
  
  \item \textbf{POC on Production Compiler}: 
  Implemented and validated proposed techniques on the MLIR-based production compiler targeting real-world software and hardware stacks.
\end{itemize}

\item \textbf{NPU Software-Hardware Co-Design}:
Actively participated in hardware definition and architectural exploration to ensure optimal SW/HW alignment for power, performance, and area (PPA).
\begin{itemize}
  \item \textbf{MAC Architecture}: 
  Evaluated trade-offs across MAC array size, SRAM bandwidth, PPE width, accumulator context size, and DSP instruction width.
  
  \item \textbf{Dynamism Support}: 
  Proposed and analyzed hardware support for dynamic shapes in transformers, enabling efficient MoE (Mixture of Experts) execution and flexible workload patching.
  
  \item \textbf{Interconnect Design}: 
  Defined tile interconnect strategies (unicast, multicast, broadcast) to balance latency, bandwidth, and scalability.
  
  \item \textbf{Memory Hierarchy Design}: 
  Contributed to memory subsystem design including size and placement of scratchpad SRAM, cache hierarchy, and DMA strategies.
\end{itemize}

\end{itemize}

\textbf{Model Compression for NPU} \\
\textit{Deep Learning Software Engineer} \hfill Intel \hfill 2018 Q4 -- 2022 Q1

\vspace{4pt}

Led model compression algorithm development for Intel's Movidius NPU, covering quantization, pruning, AutoML, and neural architecture search.

\begin{itemize}
\item \textbf{Low-bit Quantization}: Developed mixed-precision quantization pipeline (PACT, SAWB, HAQ, HAWQ) and nonlinear quantization methods for NPU deployment.

\item \textbf{Model Pruning for MLPerf}: Delivered ultra-compressed models for \textbf{MLPerf} inference benchmarks (\textbf{Resnet-50, Mobilenet, SSD-Resnet34, Bert}). On \textbf{Resnet-50}, achieved 84\% weight sparsity and 65\% activation sparsity within 1\% accuracy drop, resulting in $>$2$\times$ speedup over dense baseline.

\item \textbf{AutoML-based Quantization}: Developed a channelwise Hessian-aware trace-weighted quantization method via reinforcement learning, outperforming prior methods by $\sim$1\% top-1 accuracy.

\item \textbf{Neural Architecture Search}: Designed NPU-optimized networks --- super-resolution model 6$\times$ faster than \textbf{EDSR} with 7\% better PSNR; classification model 10\% faster than \textbf{Mobilenet-V2} with 5\% better top-1 accuracy.
\end{itemize}


\textbf{Machine Learning based Great Wall Virtual Repairing} \\
\textit{Machine Learning Engineer} \hfill Intel \hfill 2018 Q3 -- 2018 Q4
\begin{itemize}
\item Cooperated with the Chinese Foundation for Cultural Heritage Conservation. Applied 3D-GAN and texture synthesis (GAN) for AI-based structural restoration of the Great Wall.
\end{itemize}

\textbf{The Institute of Chinese Academy of Sciences} \\
\textit{Post Graduate} \hfill 2013 Q3 -- 2018 Q2
\begin{itemize}
    \item \textbf{Proprietary WiFi chip development}: Designed MAC layer and wrote Linux driver for two 802.11 chips.
    \item \textbf{ML-based SNR prediction}: Developed ML method for MAC-layer SNR prediction, improving throughput by $>$20\%. Applied model compression on LSTM for better power efficiency.
\end{itemize}


    
\end{rSection}

\begin{rSection}{Publications}{}
[1] \textbf{Xu Qian}, Victor Li, Crews Darren S, "Neural Architecture Search for Intel Movidius VPU", \textit{arxiv 2305.03739}

[2] \textbf{Xu Qian}, Victor Li, Crews Darren S, "Auto Hessian Aware Channel-wise Quantization of Neural Networks", \textit{6th Workshop on Energy Efficient Machine Learning and Cognitive Computing (EMC2 2020)}

[3] Charles Qi, Yi Wang, Hui Wang, Yang Lu, Shiva Shankar Subramanian, Finola Cahill, Conall Tuohy, Victor Li, \textbf{Xu Qian}, etc. "VPU-EM: An Event-based Modeling Framework to Evaluate NPU Performance and Power Efficiency at Scale", \textit{arxiv 2303.10271}

[4] \textbf{Xu Qian}, Bin Wu, Tianchun Ye, "QoS-aware A-MPDU retransmission scheme for 802.11 n/ac/ad WLANS", \textit{IEEE Communications Letters 21 (10), 2290-2293}

[5] \textbf{Xu Qian}, Bin Wu, Tianchun Ye, "Enhanced aggregation scheduler design in industrial 802.11 devices", \textit{Electronics Letters 53 (15), 1073-1075}

\end{rSection}

\begin{rSection}{Patents}{}
[1] Crews Darren S, Yong Jiang, Yuanyuan Li, \textbf{Xu Qian}, Peiqing Jiang, Haiyun Hong, "Methods and apparatus to accelerate convolution", \textbf{WO2023044707A1}

[2] \textbf{Xu Qian}, Yuanyuan Li, Crews Darren S, "Apparatus and method for reinforcement learning based post-training sparsification", \textbf{WO2023082278A1}

[3] \textbf{Xu Qian}, Haiyun Hong, Peiqing Jiang, Yuanyuan Li, Sijia Lou, "Apparatus, method, device and medium for accelerating computation of process engine", \textbf{WO2023092383A1}

[4] Peiqing Jiang, Yuanyuan Li, \textbf{Xu Qian}, Haiyun Hong, Yinghao Li, "Executing Matrix Multiplication By Performing Convolution With Deep Neural Network Accelerator", \textbf{WO2025184850A1}

[5] Haiyun Hong, Yuanyuan Li, \textbf{Xu Qian}, Peiqing Jiang, Yinghao Li, "Reshaping Convolution Based On Configuration Of Deep Neural Network Accelerator", \textbf{WO2025189339A1}

[6] Haiyun Hong, Umer Iftikhar Cheema, Peiqing Jiang, Yuanyuan Li, Deepak Mathaikutty, \textbf{Xu Qian}, Arnab Raha, "Streamline Processing Graph to Enhance Performance of Neural Network Execution on Hardware Accelerator", \textbf{WO2026000674A1}

[7] Yuanyuan Li, \textbf{Xu Qian}, Deepak Mathaikutty, Arnab Raha, Haiyun Hong, "Compact Configuration Descriptor Format for Neural Network Hardware Accelerator", \textbf{WO2026000671A1}

[8] Dinakar Kondru, \textbf{Xu Qian}, Yuanyuan Li, Martin-Thomas Grymel, Darren Crews, Deepak Mathaikutty, Arnab Raha, "Flexible Inter-Tile Communication in Multi-Tile Neural Network Accelerator", \textbf{WO2026000675A1}

[9] Yuanyuan Li, \textbf{Xu Qian}, Crews Darren S, Deepak Mathaikutty, Arnab Raha, Niall Hanrahan, Peiqing Jiang, "In-Place Execution Of Neural Network Operations With Scatter Write And Gather Read Across Memory Fragments", Patent Filed, In Progress

[10] \textbf{Xu Qian}, Yuanyuan Li, Crews Darren S, Zheng Qi, Deepak Mathaikutty, Raymond Sung, Arnab Raha, "Deep Neural Network Accelerator Facilitating Quantized Inference with Reduced Area and Power Consumption", Patent Filed, In Progress

[11] Yuanyuan Li, \textbf{Xu Qian}, Deepak Mathaikutty, Arnab Raha, Haiyun Hong, "A Method to Reduce Workload Overhead for LLM Execution on Resource Constrained DNN Accelerators", Patent Filed, In Progress
\end{rSection}

\end{document}

